\break
\break
\sectionTitle{Work Experiences}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
  \experience
    {Today}   {Junior Front-End Developer}{GoBild GmbH}{Munich, Bavaria, Germany.}
    {April 2021} {
                      \begin{itemize}
                        \item Creating Front End components library application for front end developers.
                        
                      \end{itemize}
                    }
                    {ReactJs, TypeScript, JavaScript, Storybook, CSS, HTML}
  \emptySeparator
  \experience
    {Today}   {General Secretary}{China Bangladesh Student Society}{Bogura, Rajshahi, Bangladesh.}
    {September 2021} {
                      \begin{itemize}
                        \item Announcement of important events and communicate to the organization.
                        
                      \end{itemize}
                    }
                    {}
  \emptySeparator
  \experience
    {August 2021} {Software Engineer Intern}{Bright
    Network}{London, England, United Kingdom.}
    {July 2021}    {
                      \begin{itemize}
                        \item I completed a remote internship in software engineering area in a company from UK.                                                                
                      \end{itemize}
                    }
                    {}
  \emptySeparator
  \experience
    {January 2021} {Research Assistant}{Aquaconsultant Ltd}{Dhaka,Bangladesh.}
    {December 2020}    {
                      \begin{itemize}
                        \item Data collection and analysis.                                                                
                      \end{itemize}
                    }
                    {ODK,Kobo}
  \emptySeparator
  \experience
    {October 2020}     {Research Assistant}{Socioconsultant Ltd}{Dhaka,Bangladesh.}
    {August 2020}    {
                      \begin{itemize}
                        \item Data collection and analysis. 
                        
                      \end{itemize}
                    }
                    {ODK,Kobo}
  \emptySeparator
  \experience
  {April 2018}       {Research Assistant }{Enrac}{Dhaka,Bangladesh.}
  {March 2018}      
                    {
                      \begin{itemize}
                        \item Data collection and analysis. 
                        
                      \end{itemize}
                    }
                    {ODK,Kobo}
  \emptySeparator

\end{experiences}
